---
title: "DATA 607 Week 7"
author: "Vinicio Haro"
date: "March 13, 2018"
output: html_document
---

Pick three of your favorite books on one of your favorite subjects. At least one of the books should have more than one author. For each book, include the title, authors, and two or three other attributes that you find interesting. Take the information that you've selected about these three books, and separately create three files which store the book's information in HTML (using an html table), XML, and JSON formats (e.g. "books.html", "books.xml", and "books.json"). Create each of these files "by hand" unless you're already very comfortable with the file formats. Your deliverable is the three source files and the R code.

Write R code, using your packages of choice, to load the information from each of the three sources into separate R data frames. Are the three data frames identical?

Identify and load in libraries
```{r}
library(httr)
library(XML)
library(jsonlite)
library(RCurl)
```

Lets start by reading in the JSON file. I used https://www.w3schools.com/js/js_json_intro.asp to learn how to manually create a JSON file. 


```{r}
json <- "https://raw.githubusercontent.com/vindication09/DATA-607-Week-7/master/books2.json"
json <- GET(json)
json <- rawToChar(json$content)
json <- fromJSON(json)
JSON <- data.frame(json)
```


Lets proceed to load in the XML file. I used https://www.w3schools.com/xml/default.asp to learn how to manually create an XML file. 
```{r}
xml <- "https://raw.githubusercontent.com/vindication09/DATA-607-Week-7/master/books.xml"
xml <- GET(xml)
xml <- rawToChar(xml$content)
xml <- xmlParse(xml)
XML <- xmlToDataFrame(xml)
```

Finally,lets proceed to load in the HTML file. As with the two previous data types, I used https://www.w3schools.com/html/ to learn how to manually create an HTML file.
```{r}
html <- "https://raw.githubusercontent.com/vindication09/DATA-607-Week-7/master/books.html"
html <- GET(html)
html <- rawToChar(html$content)
html <- htmlParse(html)
html <- readHTMLTable(html)
HTML <- data.frame(html)
```

Lets view each of the Data Frames and see how similar/different they are to each other. 
```{r}
JSON
```


```{r}
XML
```


```{r}
HTML
```

Through visual inspection, we can see that they are all the same and display the same information with equal number of columns and rows. Despite coming from seemingly different formats, r gives us the functionality to turn three different data structures into workable data frames. 

